---
title: "Russia-affiliated scholars publishing about internationalisation of higher education (based on Web of Science and OpenAlex)"
date: '2025-06-10'
categories:
  - Research notes
subtitle: 'Based on Web of Science and OpenAlex'
summary: ''
authors: [Giorgio Comai]
lastmod: '2025-06-12T09:27:26+02:00'
featured: yes
draft: no
projects: []
---



```{r setup, echo = FALSE, message=FALSE, warning=FALSE}
# https://docs.ropensci.org/openalexR/
# pak::pak("ropensci/openalexR")
# install.packages("openalexR")
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message=FALSE)
#knitr::opts_chunk$set(dev="cairo_pdf")

options(openalexR.mailto = "g@giorgiocomai.eu")
options(openalexR.message = "suppressed")
library("openalexR")
openalex_cache_folder <- fs::dir_create(fs::path_home("R", "OpenAlex_cache"))
openalex_works_by_concepts_cache_folder <- fs::dir_create(fs::path(openalex_cache_folder, "works_by_concepts"))



knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
knitr::opts_chunk$set(fig.path = "static")
#knitr::opts_chunk$set(dev="cairo_pdf")

ggplot2::theme_set(ggplot2::theme_minimal() +
                     ggplot2::theme(
                       #legend.position = "bottom",
                                    legend.title = ggplot2::element_blank(),
                                    legend.direction = "vertical",
                                    text = ggplot2::element_text(family = "Roboto Condensed",
                                                                 size = 14)))

invisible(extrafont::loadfonts(quiet = TRUE))
library(kableExtra)
```



## A preliminary note

This research note [https://doi.org/10.5281/zenodo.15722612](https://doi.org/10.5281/zenodo.15722612) relies on a combination of Clarivate's Web of Science (henceforth, WoS) and [OpenAlex](https://openalex.org/) to address the same question previously explored based on [Scopus](../2025-02-02-scopus-internationalisation-higher-education-russia/) (see also as a pdf stored on Zenodo with a stable DOI ([10.5281/zenodo.14791245](https://doi.org/10.5281/zenodo.14791245)) - or [OpenAlex alone](../2025-05-openalex-internationalisation-higher-education-russia/). 


## Objective of this research note

Outline trends in the publication record of Russia-affiliated scholars writing about internationalisation of higher education.


## Why a combination of Web of Science and OpenAlex

As this author currently does not have access to the (costly) "Web of Science Expanded API", this analysis relies on "[Web of Science Starter API](https://developer.clarivate.com/apis/wos-starter)", accessed through the "Institutional Member Plan".  

WoS Starter API allow to retrieve only basic metadata about publications; unfortunately, this does not include information about affiliation of authors that would make it possible to filter by country of affiliation. 

As this information is necessary for the purpose of this analysis, the information retrieved from the WoS API is combined with information available through OpenAlex by matching DOIs of publications. 

For a debate of the usefulness of combining information retrieved from different bibliometric APIs, see in particular Velez-Estevez et al. (2023). For a comparison of OpenAlex, Scopus and Wos, see Culbert et al. (2025).

Due to data availability issues and mismatches between the different datasets, part of the data needs to discarded, but even considering this limitations, the approach should remain substantively meaningful.

## The approach, in practice

The following sections detail all data processing steps, including all issues the determine the exclusion of part of the items originally retrieved from WoS. 

### Step 1: retrieve data from WoS Starter API


```{r setup wos}
library("keyring")

# keyring_create(keyring = "WoS", password = readr::read_lines("key.txt"))
# keyring::key_set(service = "WoS_scoper", keyring = "WoS")
keyring::keyring_unlock(keyring = "WoS")
# remotes::install_github("giocomai/scopusscoper")
library("scopusscoper")
wos_set(
  wos_base_folder = fs::path_home("R", "WoS2"),
  wos_api_key = keyring::key_get(service = "WoS_scoper",
                                 keyring = "WoS")
)
```

```{r wos_queries}

# wos_results <- wos_search(query = wos_queries[[13]])


# ihe_wos_l1 <-  wos_search(query = "TS=(higher education AND internationalization)")
# ihe_wos_l2 <-  wos_search(query = "TS=(higher education AND internationalisation)")
# 
# ihe_wos_l2 <-  wos_search(query = "TS=(\"higher education\" AND internationalisation) AND PY=2011-2024 AND DT=Article")

# available tags: https://github.com/clarivate/wosstarter_python_client

wos_queries <- c(
  "TS=(\"higher education\" AND internationalisation) AND PY=2011-2024 AND DT=Article",
  "TS=(\"higher education\" AND internationalization) AND PY=2011-2024 AND DT=Article"
)
```


```{r internationalisation_wos_df}
ihe_wos_file <- fs::path(
    wos_set()[["wos_base_folder"]],
    "ihe_wos_articles_df.rds")

if (!fs::file_exists(ihe_wos_file)) {

all_wos_results_l <- purrr::map(
  .progress = TRUE,
  .x = wos_queries,
  .f = \(current_query) {
  wos_search(query = current_query)
}) |>
purrr::list_c()

ihe_wos_df <- purrr::map(
  .progress = TRUE,
  all_wos_results_l,
  .f = \(current_wos_results) {
    tibble::tibble(
      uid = purrr::pluck(current_wos_results, "uid"),
      title = purrr::pluck(current_wos_results, "title"),
      doi = purrr::pluck(current_wos_results, "identifiers", "doi"),
      cited_by = purrr::pluck(current_wos_results, "citations", 1, "count"),
      published_year = purrr::pluck(current_wos_results, "source", "publishYear"),
      type = purrr::pluck(current_wos_results, "types", 1)
    )
  }
) |> 
  purrr::list_rbind() |> 
  dplyr::distinct(uid, .keep_all = TRUE)

# internationalisation_wos_df <- basic_wos_df |> 
#   dplyr::filter(stringr::str_detect(
#     string = title,
#     pattern = stringr::regex(pattern = "internationali(s|z)ation",
#                              ignore_case = TRUE)))

saveRDS(
  object = ihe_wos_df,
  file = ihe_wos_file
  )  
}

ihe_wos_df <- readr::read_rds(file = ihe_wos_file) |> 
  dplyr::filter(published_year< 2025)


```

The following queries are given to the WoS APIs:

```{r print wos_queries}
wos_queries
```

Based on available [fields tags](https://github.com/clarivate/wosstarter_python_client?tab=readme-ov-file), this requests all items present in WoS that:

- have both "higher education" and "internationali(s|z)ation" in either Title, Abstract, Author keywords, or Keywords Plus
- have been published between 2011 and 2024
- have "Article" as [Document type](https://webofscience.help.clarivate.com/en-us/Content/document-types.html)

These criteria reflect precisely the same criteria used in the previous analyses based on Scopus and OpenAlex. 

These queries return `r scales::number(nrow(ihe_wos_df))` unique publications.

```{r ihe_wos_doi_df}
ihe_wos_doi_df <- ihe_wos_df |> 
  dplyr::filter(!is.na(doi)) |> 
  dplyr::mutate(doi = stringr::str_to_lower(doi))
```


As we need to rely on DOIs to match these data with OpenAlex, we will need to drop all items that do not have a DOI, reducing the total to `r scales::number(nrow(ihe_wos_doi_df))`

We can then query OpenAlex to retrieve all available information about this set of DOIs. 


```{r ihe_works_from_dois_df}
options(openalexR.mailto = "g@giorgiocomai.eu")
options(openalexR.message = "suppressed")
library("openalexR")
openalex_cache_folder <- fs::dir_create(fs::path_home("R", "OpenAlex_cache"))

ihe_works_from_dois_wos_file <- fs::path(openalex_cache_folder, "ihe_works_from_dois_articles_wos.rds")

if (!fs::file_exists(ihe_works_from_dois_wos_file)) {

ihe_works_from_dois_df <- oa_fetch(
  entity = "works",
  doi = ihe_wos_doi_df$doi,
  verbose = TRUE
)  

saveRDS(object = ihe_works_from_dois_df, file = ihe_works_from_dois_wos_file)
}


ihe_works_from_dois_df <- readr::read_rds(file = ihe_works_from_dois_wos_file)  |>   dplyr::mutate(doi = stringr::str_remove(
  string = doi,
  pattern = stringr::fixed("https://doi.org/")) |> 
    stringr::str_to_lower()
)

works_all_df <- ihe_works_from_dois_df|> 
  dplyr::left_join(y = ihe_wos_doi_df  |> 
  dplyr::rename(title_wos = title,
                cited_by_wos = cited_by,
                published_year_wos = published_year,
                type_wos = type) ,
  by = "doi")
```


A small number of these DOIs are not available on OpenAlex, reducing the total to `r scales::number(nrow(works_all_df))`. Manual parsing could possibly allow to reduce slightly the number of missing matches, but considering the relatively small number of missing articles, this analysis will proceed based on a fully automated and reproducible approach.

```{r eval = FALSE}
works_all_standard_doi_df <- works_all_df |> 
                     dplyr::mutate(doi = stringr::str_remove(string = doi, pattern = stringr::fixed("https://doi.org/")) |> 
                                     stringr::str_to_lower())

ihe_wos_standard_doi_df <- ihe_wos_doi_df |> 
  dplyr::mutate(doi = stringr::str_to_lower(doi))

ihe_works_from_dois_df |> 
  dplyr::anti_join(works_all_df, 
                   by = "doi") 

nrow(ihe_wos_standard_doi_df) - nrow(works_all_df)

```

OpenAlex would identify some of these items as something that is not a journal article (`r works_all_df |> dplyr::filter(type != "article") |> nrow()` items in total), mostly categorising them as book chapters. It would also record the publication year before 2011 for `r works_all_df |> dplyr::filter(publication_year < 2011) |> nrow()` items. But for the purpose of this analysis, we will trust WoS and keep all items retrieved from WoS that match the above query, have a doi, and that doi corresponds to an item available on OpenAlex. The vast majority of items retrieved from WoS remain part of these analysis even accounting for data quality issues.

```{r eval = FALSE}
works_all_df |> 
  dplyr::filter(type != "article") |> 
  dplyr::group_by(type) |> 
  dplyr::count()



works_all_df |> dplyr::filter(publication_year < 2011)

works_all_df |> 
  dplyr::filter(publication_year > 2024)
```



```{r works_df}

# works_df <- works_all_df |> 
#   dplyr::filter(type == "article") |> 
#   dplyr::filter(publication_year>=2011) |> 
#   dplyr::filter(publication_year<=2024)
#nrow(works_df)

works_df <- works_all_df 
```




```{r affiliation_df}
authorship_df <- works_df |> 
  dplyr::select(id, authorships, cited_by_count, cited_by_wos) |> 
  dplyr::rename(work_id = id) |> 
  tidyr::unnest(authorships) |> 
  dplyr::rename(author_id = id,
                author_display_name = display_name)

affiliation_pre_df <- works_df |> 
  dplyr::select(id, authorships) |> 
  dplyr::rename(work_id = id) |> 
  tidyr::unnest(authorships) |> 
  dplyr::rename(author_id = id,
                author_display_name = display_name) |> 
  tidyr::unnest(affiliations) |> 
  dplyr::rename(affiliation_id = id,
                affiliation_display_name = display_name,
                affiliation_country_code = country_code) |> 
  dplyr::group_by(author_id) |> 
  dplyr::mutate(
    affiliation_name_combo = stringr::str_flatten(unique(affiliation_display_name),
                                                  collapse = "; ")) |> 
  dplyr::ungroup() 

affiliation_ru_only_pre_df <- works_df |> 
  dplyr::select(id, authorships) |> 
  dplyr::rename(work_id = id) |> 
  tidyr::unnest(authorships) |> 
  dplyr::rename(author_id = id,
                author_display_name = display_name) |> 
  tidyr::unnest(affiliations) |> 
  dplyr::rename(affiliation_id = id,
                affiliation_display_name = display_name,
                affiliation_country_code = country_code) |> 
  dplyr::filter(!is.na(affiliation_country_code)) |> 
  dplyr::filter(affiliation_country_code=="RU") |> 
  dplyr::group_by(author_id) |> 
  dplyr::mutate(
    affiliation_name_combo = stringr::str_flatten(unique(affiliation_display_name),
                                                  collapse = "; ")) |> 
  dplyr::ungroup() 


authorship_ru_only_df <- 
  affiliation_ru_only_pre_df |> 
  dplyr::distinct(work_id) |> 
  dplyr::left_join(
    works_df |> 
      dplyr::select(id, authorships, cited_by_count, cited_by_wos) |> 
      dplyr::rename(work_id = id),
    by = "work_id"  
  ) |> 
  tidyr::unnest(authorships) |> 
  dplyr::rename(author_id = id,
                author_display_name = display_name)

by_author_count_ru_only_df <- affiliation_ru_only_pre_df |> 
  dplyr::distinct(work_id, author_id) |> 
  dplyr::group_by(author_id) |> 
  dplyr::count() |> 
  dplyr::ungroup()

by_author_count_df <- authorship_df |> 
  dplyr::distinct(work_id, author_id) |> 
  dplyr::group_by(author_id) |> 
  dplyr::count() |> 
  dplyr::ungroup()

by_author_citation_count_df <- authorship_df |> 
  dplyr::distinct(work_id, author_id, cited_by_count, cited_by_wos) |> 
  dplyr::group_by(author_id) |> 
  dplyr::summarise(
    cited_by_oa = sum(cited_by_count),
    cited_by_wos = sum(cited_by_wos)
  ) |> 
  dplyr::ungroup()

by_author_citation_count_ru_only_df <- authorship_ru_only_df |> 
  dplyr::distinct(work_id, author_id, cited_by_count, cited_by_wos) |> 
  dplyr::group_by(author_id) |> 
  dplyr::summarise(
    cited_by_oa = sum(cited_by_count),
    cited_by_wos = sum(cited_by_wos)
  ) |> 
  dplyr::ungroup()


affiliation_df <- affiliation_pre_df |> 
  dplyr::left_join(y = by_author_count_df, by = "author_id") |> 
  dplyr::left_join(y = by_author_citation_count_df, by = "author_id")


affiliation_ru_only_df <- affiliation_ru_only_pre_df |> 
  dplyr::left_join(y = by_author_count_ru_only_df, by = "author_id") |> 
  dplyr::left_join(y = by_author_citation_count_ru_only_df, by = "author_id")


```


```{r ru_affiliation_df}
ru_affiliation_df <- affiliation_df |> 
  dplyr::filter(!is.na(affiliation_country_code)) |> 
  dplyr::distinct(work_id, affiliation_country_code) |> 
  dplyr::group_by(work_id) |> 
  dplyr::summarise(ru_affiliation = dplyr::if_else(
    condition = "RU" %in% affiliation_country_code,
    true = "Russian affiliation",
    false = "No Russian affiliation",
    missing = "Affiliation not available"
  ))

# na_affiliation_df <- affiliation_df |> 
#   dplyr::filter(is.na(affiliation_country_code)) |> 
#   dplyr::distinct(work_id, affiliation_country_code, .keep_all = TRUE) 
# 
# works_df |> 
#   dplyr::rename(work_id = id) |>  
#   dplyr::anti_join(y = affiliation_df, by = "work_id") 
```


```{r works_ru_long_df}
works_ru_long_df <- works_df |> 
  dplyr::rename(work_id = id) |> 
  # dplyr::filter(publication_year>2010,
  #               publication_year<2025,
  #                 type == "article") |> 
  dplyr::left_join(ru_affiliation_df, by = "work_id") |> 
  #dplyr::filter(!is.na(ru_affiliation)) |> 
  dplyr::select(-publication_year) |> 
  dplyr::rename(publication_year = published_year_wos) |> 
  dplyr::group_by(publication_year, ru_affiliation) |> 
  dplyr::count() |> 
  dplyr::ungroup() |> 
  tidyr::complete(publication_year, ru_affiliation, fill = list(n = 0)) |> 
  tidyr::replace_na(replace = list(ru_affiliation = "Affiliation not available"))

```


```{r works_ru_long_df gt}

works_ru_long_df |> 
  tidyr::pivot_wider(names_from = ru_affiliation, values_from = n) |> 
  dplyr::mutate(Total = `Russian affiliation`+`No Russian affiliation`+ `Affiliation not available`) |> 
  dplyr::mutate(`Russian affiliation share` = `Russian affiliation`/sum(`Russian affiliation`, `No Russian affiliation`)) |> 
  dplyr::mutate(`Russian affiliation share` = scales::percent(`Russian affiliation share`, accuracy = 0.01)) |> 
  dplyr::rename(`Publication year` = publication_year) |> 
    gt::gt(caption = "Publications found through WoS that include both `internationalisation' and 'higher education` that are also available on OpenAlex with the same doi; Russian affiliation recorded if at least one co-author has a Russian affiliation; Russian affiliation share calculated only when affiliation was available.") |> 
      gt::grand_summary_rows(
    columns = c(`No Russian affiliation`, `Russian affiliation`, `Affiliation not available`, Total),
    fns = list(
      Total = ~sum(.)
    )
    )


```

```{r totals_n}

total_ru_n <- works_ru_long_df |> 
  dplyr::filter(ru_affiliation == "Russian affiliation") |> 
  dplyr::pull(n) |> 
  sum()

total_no_ru_n <- works_ru_long_df |> 
  dplyr::filter(ru_affiliation == "No Russian affiliation") |> 
  dplyr::pull(n) |> 
  sum()

total_na_n <- works_ru_long_df |> 
  dplyr::filter(ru_affiliation == "Affiliation not available") |> 
  dplyr::pull(n) |> 
  sum()

total_n <- works_ru_long_df |> 
  dplyr::pull(n) |> 
  sum()
```


In brief, the `r scales::number(total_n)` journal articles identified via WoS and available on OpenAlex include:

- `r scales::number(total_ru_n)` articles with at least an author with a Russian affiliation
- `r scales::number(total_no_ru_n)` articles with no author with a Russian affiliation
- `r scales::number(total_na_n)` articles where the affiliation is not available (or, in a small number of cases, the country of the affiliation is not available)


```{r ru_no_ru_gg}
base_df <- works_ru_long_df |> 
  dplyr::rename(Affiliation = ru_affiliation, 
                year = publication_year)


no_ru_gg <- base_df |> dplyr::filter(Affiliation == "No Russian affiliation") |> 
 ggplot2::ggplot() +
  ggplot2::geom_col(mapping = ggplot2::aes(x = year, y = n)) +
    ggplot2::scale_x_continuous(name = NULL, breaks = seq.int(from = 2011, to = 2024, by = 3)) +
  ggplot2::scale_y_continuous(name = "Number of publications", labels = scales::number) +
  ggplot2::labs(title = "No Russian affiliation") +
    ggplot2::theme(plot.title = ggplot2::element_text(hjust = 0.5))

ru_gg <- base_df |> dplyr::filter(Affiliation == "Russian affiliation") |> 
 ggplot2::ggplot() +
  ggplot2::geom_col(mapping = ggplot2::aes(x = year, y = n))+
    ggplot2::scale_x_continuous(name = NULL, breaks = seq.int(from = 2011, to = 2024, by = 3)) +
  ggplot2::scale_y_continuous(name = NULL, labels = scales::number) +
  ggplot2::labs(title = "Russian affiliation") +
    ggplot2::theme(plot.title = ggplot2::element_text(hjust = 0.5))

library("patchwork")

no_ru_gg +
  ru_gg  + 
  plot_annotation(    title = "Number of publications about internationalisation of higher education",
    subtitle = "Counting relevant journal publications identified by Web of Science\nAffiliation attributed based on OpenAlex data",
    caption =  stringr::str_c("* ", sQuote('Russian affiliation'), " attributed if at least one author is affiliated with a Russia-based institution", "\nNot included when affiliation is not available or could not be attributed to any country."))
```




## Focus on publications by scholars with a Russian affiliation

N.B. the following tables report only data related to articles published with a Russian affiliation; if the same author has published other articles about internationalisation of higher education, but not with a Russian affiliation, this is not included in this section.

```{r ru_affiliations_df}
ru_affiliations_df <- affiliation_ru_only_df |> 
  dplyr::filter(!is.na(affiliation_country_code)) |> 
  dplyr::filter(affiliation_country_code == "RU") 

```

### By author

Authors of scholarly articles associated with 'internationalisation of higher education' published with a Russian affiliation. Ordered by number of publications; click on the `cited by` column to order by number of times cited; as expected, OpenAlex and Web of Science report slightly different figures. The `works` column link to the page dedicated to the article on OpenAlex, including a complete set of metadata and a link to the article itself (usually, shown right under the title, as a button with "html" and/or "pdf").


```{r ru_affiliations_df_gt}
ru_affiliations_df_gt <- ru_affiliations_df |>
      dplyr::mutate(
    works = purrr::map2_chr(
    .x = stringr::str_remove(work_id, "https://openalex.org/"),
    .y = work_id,
    .f = \(x,y) {
      htmltools::a(x,
                   href = y) |> as.character()
    } 
     )
    ) |> 
  dplyr::group_by(author_id) |> 
  #dplyr::select(works) |> 
  dplyr::mutate(works = stringr::str_flatten(works, collapse = "; ")) |> 
  dplyr::ungroup() |> 
  dplyr::distinct(author_id, .keep_all = TRUE) |> 
  # dplyr::left_join(
  #   y = affiliation_df |> 
  #     dplyr::distinct(author_id, author_display_name, affiliation_name_combo, cited_by_total),
  #   by = "author_id") |> 
 # dplyr::filter(n>2) |> 
  dplyr::mutate(
    author = purrr::map2_chr(
    .x = author_display_name,
    .y = author_id,
    .f = \(x,y) {
      htmltools::a(x,
                   href = stringr::str_c("https://openalex.org/authors/",
                   y |> stringr::str_remove(pattern = stringr::fixed("https://openalex.org/")))
                   ) |> as.character()
    } 
     )
    ) |>
  dplyr::select(author, affiliation_name_combo, n, cited_by_wos, cited_by_oa, works) |> 
  dplyr::arrange(dplyr::desc(n),
                 dplyr::desc(cited_by_wos)
                 ) |> 
  dplyr::rename(affiliation = affiliation_name_combo, 
                items = n, 
                `cited by (WoS)` = cited_by_wos,
                `cited by (OpenAlex)` = cited_by_oa
                ) |> 
    gt::gt(caption = "Authors of scholarly articles associated with 'internationalisation of higher education' published with a Russian affiliation. Ordered by number of publications; click on the `cited by` column to order by number of times cited.") |>gt::cols_width(
      `items` ~ gt::px(55),
      `affiliation` ~ gt::px(150),
      `cited by (WoS)` ~ gt::px(100),
      `cited by (OpenAlex)` ~ gt::px(110)
      # ,
      # `cited by` ~ gt::px(120)
               ) |> 
   gt::opt_interactive(active = TRUE, use_pagination = TRUE, use_sorting = TRUE, page_size_default = 3, use_page_size_select = TRUE) |> 
  gt::fmt_markdown(columns = c(author, works))
  
gt::gtsave(data = ru_affiliations_df_gt, filename = "ru_affiliations_df_gt.html")
  
  
# htmlwidgets::saveWidget(
#   widget = ru_affiliations_df_gt,
#   file = "ru_affiliations_df_gt.html",
#   selfcontained = TRUE)
#reactable::reactable(sortable = TRUE)

  
  # knitr::kable(booktabs = TRUE,escape = FALSE,
  #              caption = "Authors of scholarly articles associated with 'internationalisation of higher education' published with a Russian affiliation and more than two publications")
  # 


htmltools::includeHTML("ru_affiliations_df_gt.html")


  

```

### By institution

Russian institutions where scholars who published about 'internationalisation of higher education' were affiliated with. Ordered by number of publications; click on the `cited by` column to order by number of times cited.

```{r by_institution}
ru_affiliations_by_institution_df <- ru_affiliations_df |> 
        dplyr::mutate(
    works = purrr::map2_chr(
    .x = stringr::str_remove(work_id, "https://openalex.org/"),
    .y = work_id,
    .f = \(x,y) {
      htmltools::a(x,
                   href = y) |> as.character()
    } 
     )
    ) |> 
  dplyr::group_by(affiliation_id) |> 
  #dplyr::select(works) |> 
  dplyr::mutate(works = stringr::str_flatten(unique(works), collapse = "; ")) |> 
  dplyr::ungroup() |> 
  dplyr::distinct(work_id, affiliation_id, affiliation_display_name, works) |> 
  dplyr::left_join(works_df |> 
                     dplyr::rename(work_id = id) |> 
                     dplyr::select(work_id, cited_by_count, cited_by_wos),
                   by = "work_id") |> 
  dplyr::group_by(affiliation_id, affiliation_display_name, works) |> 
    dplyr::summarise(
    cited_by_oa = sum(cited_by_count),
    cited_by_wos = sum(cited_by_wos),
    publications = dplyr::n()
  ) |> 
  dplyr::ungroup() |> 
  dplyr::arrange(dplyr::desc(cited_by_wos)) 


ru_affiliations_by_institution_df_gt <- ru_affiliations_by_institution_df |> 
  dplyr::mutate(
    affiliation_display_name = purrr::map2_chr(
      .x = affiliation_display_name,
      .y = affiliation_id,
      .f = \(x,y) {
        htmltools::a(x,
                     href = stringr::str_c("https://openalex.org/works?filter=concepts.id:c2778011250,publication_year:2011-2024,type:types/article,authorships.institutions.lineage:",
                                           y |> stringr::str_remove(pattern = stringr::fixed("https://openalex.org/")))
        ) |> as.character()
      } 
    )
  ) |> 
  dplyr::rename(affiliation = affiliation_display_name,
                                items = publications, 
                `cited by (WoS)` = cited_by_wos,
                `cited by (OpenAlex)` = cited_by_oa) |> 
  dplyr::select(affiliation, items,`cited by (WoS)`,  `cited by (OpenAlex)`, works) |> 
gt::gt(caption = "Authors affiliated with these Russia-based institutions have published about 'internationalisation of higher education'") |> 
  gt::cols_width(
      `items` ~ gt::px(55),
      `affiliation` ~ gt::px(200),
      `cited by (WoS)` ~ gt::px(100),
      `cited by (OpenAlex)` ~ gt::px(110)
  ) |> 
  gt::opt_interactive(active = TRUE, use_pagination = TRUE, use_sorting = TRUE, page_size_default = 3, use_page_size_select = TRUE) |> 
  gt::fmt_markdown(columns = c(affiliation, works))

gt::gtsave(data = ru_affiliations_by_institution_df_gt,
           filename = "ru_affiliations_by_institution_df_gt.html")

htmltools::includeHTML("ru_affiliations_by_institution_df_gt.html")
```


## References

Culbert, Jack H., Anne Hobert, Najko Jahn, Nick Haupka, Marion Schmidt, Paul Donner, and Philipp Mayr. 2025. ‘Reference Coverage Analysis of OpenAlex Compared to Web of Science and Scopus’. Scientometrics 130 (4): 2475–92. https://doi.org/10.1007/s11192-025-05293-3.


Velez-Estevez, A., I. J. Perez, P. García-Sánchez, J. A. Moral-Munoz, and M. J. Cobo. 2023. ‘New Trends in Bibliometric APIs: A Comparative Analysis’. Information Processing & Management 60 (4): 103385. https://doi.org/10.1016/j.ipm.2023.103385.
