---
title: "Russia-affiliated scholars publishing about internationalisation of higher education (based on OpenAlex)"
date: '2025-05-14'
categories:
  - Research notes
subtitle: 'A quantitative investigation based on OpenAlex'
summary: ''
authors: [Giorgio Comai]
lastmod: '2025-05-14T09:27:26+02:00'
featured: yes
draft: no
projects: []
---



```{r setup, echo = FALSE, message=FALSE, warning=FALSE}
# https://docs.ropensci.org/openalexR/
# pak::pak("ropensci/openalexR")
# install.packages("openalexR")
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message=FALSE)
#knitr::opts_chunk$set(dev="cairo_pdf")

options(openalexR.mailto = "g@giorgiocomai.eu")
options(openalexR.message = "suppressed")
library("openalexR")
openalex_cache_folder <- fs::dir_create(fs::path_home("R", "OpenAlex_cache"))
openalex_works_by_concepts_cache_folder <- fs::dir_create(fs::path(openalex_cache_folder, "works_by_concepts"))



knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
knitr::opts_chunk$set(fig.path = "static")
#knitr::opts_chunk$set(dev="cairo_pdf")

ggplot2::theme_set(ggplot2::theme_minimal() +
                     ggplot2::theme(
                       #legend.position = "bottom",
                                    legend.title = ggplot2::element_blank(),
                                    legend.direction = "vertical",
                                    text = ggplot2::element_text(family = "Roboto Condensed",
                                                                 size = 14)))

invisible(extrafont::loadfonts(quiet = TRUE))
library(kableExtra)
```



```{r n_concepts}
n_concepts_file <- fs::path(openalex_cache_folder, "n_concepts.rds")

if (!fs::file_exists(n_concepts_file)) {
  concepts_resp <- httr2::request(base_url = "https://api.openalex.org/concepts") |>
    httr2::req_headers(
      "Accept" = "application/json"
    ) |> httr2::req_perform() |> 
    httr2::resp_body_json()
  
  n_concepts <- as.numeric(concepts_resp$meta$count)
  saveRDS(object = n_concepts, file = n_concepts_file)
}

n_concepts <- readr::read_rds(n_concepts_file)


```


## A preliminary note

This research note relies on [OpenAlex](https://openalex.org/) to address the same question previously explored based on Scopus. 

See the previous note [in a web-version](https://giorgiocomai.eu/post/2025-02-02-scopus-internationalisation-higher-education-russia/) or as a pdf stored on Zenodo with a stable DOI ([10.5281/zenodo.14791245](https://doi.org/10.5281/zenodo.14791245)). 

## Objective of this research note

Outline trends in the publication record of Russia-affiliated scholars writing about internationalisation of higher education.

## Relying on OpenAlex's categorisation

OpenAlex automatically associated each publication to one or more concepts. Luckily, among the `r scales::number(n_concepts)` concepts included in OpenAlex as of this writing, there is one which perfectly aligns with the objectives of this research note:

- [concept c2778011250: Internationalization of Higher Education](https://openalex.org/concepts/c2778011250)

Concepts are attributed to articles based on title, abstract, as well as the publication venue. For more details, see [the official documentation](https://docs.openalex.org/api-entities/concepts#how-concepts-are-assigned).


```{r works_df}

current_concept <- "c2778011250"

current_concept_file <- fs::path(
  openalex_works_by_concepts_cache_folder, 
  fs::path_ext_set(current_concept,ext = "rds"))

if (!fs::file_exists(current_concept_file)) {
  works_df <- oa_fetch(
  entity = "works",
  concepts.id = current_concept,
  count_only = FALSE,
  verbose = FALSE,
  output = "tibble"
)
  
  attr(works_df, "retrieved_at") <- Sys.time()
  
  saveRDS(object = works_df,
          file = current_concept_file)
}

works_df <- readr::read_rds(file = current_concept_file)

```

OpenAlex includes a total of `r scales::number(nrow(works_df))` works about "Internationalization of Higher Education":

```{r}
works_df |> 
  dplyr::group_by(type) |> 
  dplyr::count() |> 
  dplyr::ungroup() |> 
  gt::gt(caption = "Works associated with 'Internationalization of Higher Education' by type") |> 
  gt::grand_summary_rows(
    columns = c(n),
    fns = list(
      total = ~sum(.)
    )
    )

```

For consistency with the previous, Scopus-based analysis, we will focus exclusively on journal articles published between 2011 and 2024.





```{r affiliation_df}
affiliation_df <- works_df |> 
  dplyr::select(id, authorships, cited_by_count) |> 
  dplyr::rename(work_id = id) |> 
  tidyr::unnest(authorships) |> 
  dplyr::rename(author_id = id,
                author_display_name = display_name) |> 
  tidyr::unnest(affiliations) |> 
  dplyr::rename(affiliation_id = id,
                affiliation_display_name = display_name,
                affiliation_country_code = country_code) |> 
  dplyr::group_by(author_id) |> 
  dplyr::mutate(
    affiliation_name_combo = stringr::str_flatten(unique(affiliation_display_name), collapse = "; "), 
    cited_by_total = sum(cited_by_count)) |> 
  dplyr::ungroup()
```


```{r ru_affiliation_df}
ru_affiliation_df <- affiliation_df |> 
  dplyr::filter(!is.na(affiliation_country_code)) |> 
  dplyr::distinct(work_id, affiliation_country_code) |> 
  dplyr::group_by(work_id) |> 
  dplyr::summarise(ru_affiliation = dplyr::if_else(
    condition = "RU" %in% affiliation_country_code,
    true = "Russian affiliation",
    false = "No Russian affiliation",
    missing = "Affiliation not available"
  ))

# na_affiliation_df <- affiliation_df |> 
#   dplyr::filter(is.na(affiliation_country_code)) |> 
#   dplyr::distinct(work_id, affiliation_country_code, .keep_all = TRUE) 
# 
# works_df |> 
#   dplyr::rename(work_id = id) |>  
#   dplyr::anti_join(y = affiliation_df, by = "work_id") 
```


```{r works_ru_long_df}
works_ru_long_df <- works_df |> 
  dplyr::rename(work_id = id) |> 
  dplyr::filter(publication_year>2010,
                publication_year<2025,
                  type == "article") |> 
  dplyr::left_join(ru_affiliation_df, by = "work_id") |> 
  #dplyr::filter(!is.na(ru_affiliation)) |> 
  dplyr::group_by(publication_year, ru_affiliation) |> 
  dplyr::count() |> 
  dplyr::ungroup() |> 
  tidyr::complete(publication_year, ru_affiliation, fill = list(n = 0)) |> 
  tidyr::replace_na(replace = list(ru_affiliation = "Affiliation not available"))

```


```{r}

works_ru_long_df |> 
  tidyr::pivot_wider(names_from = ru_affiliation, values_from = n) |> 
  dplyr::mutate(Total = `Russian affiliation`+`No Russian affiliation`+ `Affiliation not available`) |> 
  dplyr::mutate(`Russian affiliation share` = `Russian affiliation`/sum(`Russian affiliation`, `No Russian affiliation`)) |> 
  dplyr::mutate(`Russian affiliation share` = scales::percent(`Russian affiliation share`, accuracy = 0.01)) |> 
  dplyr::rename(`Publication year` = publication_year) |> 
    gt::gt(caption = "Publications categorised under `internationalisation of higher education` by OpenAlex including information on affiliation; Russian affiliation recorded if at least one co-author has a Russian affiliation; Russian affiliation share calculated only when affiliation was available.") |> 
      gt::grand_summary_rows(
    columns = c(`No Russian affiliation`, `Russian affiliation`, `Affiliation not available`, Total),
    fns = list(
      Total = ~sum(.)
    )
    )


```

```{r totals_n}

total_ru_n <- works_ru_long_df |> 
  dplyr::filter(ru_affiliation == "Russian affiliation") |> 
  dplyr::pull(n) |> 
  sum()

total_no_ru_n <- works_ru_long_df |> 
  dplyr::filter(ru_affiliation == "No Russian affiliation") |> 
  dplyr::pull(n) |> 
  sum()

total_na_n <- works_ru_long_df |> 
  dplyr::filter(ru_affiliation == "Affiliation not available") |> 
  dplyr::pull(n) |> 
  sum()

total_n <- works_ru_long_df |> 
  dplyr::filter(ru_affiliation == "Affiliation not available") |> 
  dplyr::pull(n) |> 
  sum()
```


In brief, OpenAlex identifies `r scales::number(total_n)` journal articles, including:

- `r scales::number(total_ru_n)` articles with at least an author with a Russian affiliation
- `r scales::number(total_no_ru_n)` articles with no author with a Russian affiliation
- `r scales::number(total_na_n)` articles where the affiliation is not available (or, in a small number of cases, the country of the affiliation is not available)



```{r ru_no_ru_gg}
base_df <- works_ru_long_df |> 
  dplyr::rename(Affiliation = ru_affiliation, 
                year = publication_year)


no_ru_gg <- base_df |> dplyr::filter(Affiliation == "No Russian affiliation") |> 
 ggplot2::ggplot() +
  ggplot2::geom_col(mapping = ggplot2::aes(x = year, y = n)) +
    ggplot2::scale_x_continuous(name = NULL, breaks = seq.int(from = 2011, to = 2024, by = 3)) +
  ggplot2::scale_y_continuous(name = "Number of publications", labels = scales::number) +
  ggplot2::labs(title = "No Russian affiliation") +
    ggplot2::theme(plot.title = ggplot2::element_text(hjust = 0.5))

ru_gg <- base_df |> dplyr::filter(Affiliation == "Russian affiliation") |> 
 ggplot2::ggplot() +
  ggplot2::geom_col(mapping = ggplot2::aes(x = year, y = n))+
    ggplot2::scale_x_continuous(name = NULL, breaks = seq.int(from = 2011, to = 2024, by = 3)) +
  ggplot2::scale_y_continuous(name = NULL, labels = scales::number) +
  ggplot2::labs(title = "Russian affiliation") +
    ggplot2::theme(plot.title = ggplot2::element_text(hjust = 0.5))

library("patchwork")

no_ru_gg +
  ru_gg  + 
  plot_annotation(    title = "Number of publications about internationalisation of higher education",
    subtitle = "Counting relevant journal publications identified by OpenAlex",
    caption =  stringr::str_c("* ", sQuote('Russian affiliation'), " attributed if at least one author is affiliated with a Russia-based institution"))
```



## Focus on publications by scholars with a Russian affiliation

It is possible to explore this subset of publications through OpenAlex's interactive dashboard [following this link](https://openalex.org/works?filter=concepts.id%3Ac2778011250,authorships.countries%3Acountries%2Fru,publication_year%3A2011-2024,type%3Atypes%2Farticle&page=1).

```{r ru_affiliations_df}
ru_affiliations_df <- affiliation_df |> 
  dplyr::filter(!is.na(affiliation_country_code)) |> 
  dplyr::filter(affiliation_country_code == "RU") 
```


```{r ru_affiliations_df_gt}
ru_affiliations_df_gt <- ru_affiliations_df |> 
  dplyr::group_by(author_id) |> 
  dplyr::count(sort = TRUE) |> 
  dplyr::ungroup() |> 
  dplyr::left_join(
    affiliation_df |> 
      dplyr::distinct(author_id, author_display_name, affiliation_name_combo, cited_by_total),
    by = "author_id") |> 
 # dplyr::filter(n>2) |> 
  dplyr::mutate(author = purrr::map2_chr(
    .x = author_display_name,
    .y = author_id,
    .f = \(x,y) {
      htmltools::a(x, href = y) |> as.character()
    }  )) |>
  dplyr::select(author, affiliation_name_combo, n, cited_by_total) |> 
  dplyr::rename(affiliation = affiliation_name_combo, 
                publications = n, 
                `cited by` = cited_by_total) |> 
    gt::gt(caption = "Authors of scholarly articles associated with 'internationalisation of higher education' published with a Russian affiliation and more than two publications") |>gt::cols_width(
      `publications` ~ gt::px(120),
      `cited by` ~ gt::px(120)
               ) |> 
   gt::opt_interactive(active = TRUE, use_pagination = TRUE, use_sorting = TRUE, page_size_default = 3, use_page_size_select = TRUE) |> 
  gt::fmt_markdown(columns = author)
  
gt::gtsave(data = ru_affiliations_df_gt, filename = "ru_affiliations_df_gt.html")
  
  
# htmlwidgets::saveWidget(
#   widget = ru_affiliations_df_gt,
#   file = "ru_affiliations_df_gt.html",
#   selfcontained = TRUE)
#reactable::reactable(sortable = TRUE)

  
  # knitr::kable(booktabs = TRUE,escape = FALSE,
  #              caption = "Authors of scholarly articles associated with 'internationalisation of higher education' published with a Russian affiliation and more than two publications")
  # 


htmltools::includeHTML("ru_affiliations_df_gt.html")

```

### By institution

```{r by_institution}
ru_affiliations_df |> 
  dplyr::distinct(work_id, affiliation_id, affiliation_display_name) |> 
  dplyr::left_join(works_df |> 
  dplyr::rename(work_id = id) |> 
  dplyr::select(work_id, cited_by_count),
  by = "work_id") |> 
  dplyr::group_by(affiliation_id, affiliation_display_name) |> 
  dplyr::summarise(cited_by_count = sum(cited_by_count), 
                   publications = dplyr::n()) |> 
  dplyr::ungroup() |> 
  dplyr::arrange(dplyr::desc(cited_by_count)) |> 
  gt::gt(caption = "Authors affiliated with these Russia-based institutions have published about 'internationalisation of higher education'")

```

### By article

```{r by_article}
ru_affiliations_df |> 
  dplyr::distinct(work_id) |> 
  dplyr::left_join(works_df |> 
  dplyr::rename(work_id = id) |> 
  dplyr::select(work_id, title, publication_year, cited_by_count, source_display_name),
  by = "work_id") |> 
  dplyr::arrange(dplyr::desc(cited_by_count), publication_year) |>
  dplyr::rename(journal = source_display_name) |> 
  gt::gt(caption = "List of articles with a Russian affiliation")


```

